A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Add BDDf and OBDD relationship

Before discussing the symbolic model checking algorithms \texttt{BDD}$_f$ and
\texttt{BDD}$_R$, the used $\mu$-Calculus has to be described. For a given finite
signature $\mathcal{S}$, each symbol is either an individual or a predicate
variable having positive arity. Burch et al.~\cite{BURCH90} considered two
syntactic categories, i.e. \textit{formulas} and \textit{relational terms}, having
the following forms.

@@

Finally, after defining the $\mu$-Calculus formally, the model checking algorithms
can be described. They operate on the limited Boolean domain, i.e.
$D = \lbrace 0, 1 \rbrace$ but Burch et al.~\cite{BURCH90} also described how any
\textit{finite} domain can be encoded into this limited Boolean domain. This last
fact generalizes the introduced algorithms to any \textit{finite} domain. \tbr

>>>>

Before discussing the symbolic model checking algorithms $\text{BDD}_f$ and
$\text{BDD}_R$, the used $\mu$-Calculus has to be described. For a given finite
signature $\mathcal{S}$, each symbol is either an individual or a predicate
variable having positive arity. Burch et al.~\cite{BURCH90} considered two
syntactic categories, i.e. \textit{formulas} and \textit{relational terms}, having
the following forms.

@@

Finally, after defining the $\mu$-Calculus formally, the model checking algorithms
can be described. They operate on the limited Boolean domain, i.e.
$D = \lbrace 0, 1 \rbrace$ but Burch et al.~\cite{BURCH90} also described how any
\textit{finite} domain can be encoded into this limited Boolean domain. This last
fact generalizes the introduced algorithms to any \textit{finite} domain.

They described two function representing the algorithm:
$\text{BDD}_f \left( f, I_P \right)$ and $\text{BDD}_R \left( R, I_P \right)$,
where $f$ and $R$ denote a formula and a relational term, respectively. For 
$\text{BDD}_f$, $I_P$ represents a relational variable interpretation assigning
values to free relational variables in $f$~\cite{BURCH90}.

A given individual variable interpretation $I_D$ satisfies \newline
$\text{BDD}_f \left( f, I_P \right)$ iff $f$ is satisfied by $\mathcal{M}$ having
interpretations $I_P$ and $I_D$. OBDDs in combination with place-holder variables
$d_1, \ldots, d_n$ are used to represent the values of the relational variables
$\in I_P$. $d_i$ represents the $i^{th}$ argument of a relation and an $n$-ary
relation holds for arguments $y_1, \ldots, y_n$ iff the interpretation
$\langle d_1 \leftarrow y_1, \ldots, d_n \leftarrow y_n \rangle$ satisfies the
OBDD.

\tbr
